Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2019-08-26 Manuscript/manuscript.Rmd
Results edits

## DEVELOPING A RESOLUTION-SPECIFIC APPROACH FOR DATA CONSTRUCTION

We analyzed publically available replicate Hi-C data sets from the GM12878 and K562 cell lines (Supplementary Table 1). Topologically associating domains (TADs) were subsequently called using the ARROWHEAD pipeline [@durand2016juicer] at 5 data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb. After removing TADs that exceeded 2 megabases in length, we obtained a total of 16133, 14824, 8081, 3560, and 919 unique TAD boundaries for the GM12878 cell line, and 9314, 10881, 6923, 3197, and 831 unique TAD boundaries for the K562 cell line across each of the 5 resolutions respectively (Supplementary Figure 1). To account for the variability in boundary location due to varying resolution, we developed a resolution-specific approach toward constructing TAD versus non-TAD boundary regions on the linear genome (See Methods), labeled as a response vector **Y** (Figure 1A). TAD boundary regions were defined as regions on the linear genome where a genomic bin overlapped with a flanked TAD boundary ($Y = 1$), while non-TAD boundary regions were defined as the regions that did not overlap with a flanked TAD boundary ($Y = 0$). A significant number of TAD boundary regions were found to be specific to one of the two cell lines (Supplementary Figure 2). Given the plasticity in boundary location, we opted to build cell line specific models for predicting TAD boundary regions. The results presented are for the GM12878 cell line, with K562 results presented in the supplementary materials.

![**Illustrating the resolution-specific data construction and feature engineering used for downstream modeling.** (A) Unique boundaries are denoted by the blue dots. The yellow regions denote the flanked boundary regions according to the Hi-C data resolution (i.e. 100 kb resolution corresponded to a 100 kb flank for a total boundary region of 200 kb). The linear genome was subsequently binned into resolution-specific intervals. The response vector **Y** was defined as a genomic bin that either overlapped with a flanked TAD boundary ($Y = 1$) or did not ($Y = 0$). (B) Three types of associations between TAD boundaries and genomic annotations were used to build the feature space including _Overlap Counts_ (OC), _Overlap Percent_ (OP), and ($log_{2}$) _Distance_. The green shapes denote regions defined by a specific functional genomic annotation used for feature engineering. ](Figures/model_construction_and_predictor_types.png)

## PROPORTIONAL IMBALANCE REMAINED SEVERE IRRESPECTIVELY OF Hi-C DATA RESOLUTION

We then investigated the proportional class imbalance (PI) featured at each resolution. The PI was defined as the ratio of TAD boundary regions ($Y=1$) versus the sum of both TAD and non-TAD boundary regions for each chromosome specific sections of the linear genome and has a range from 0 to 0.5. The PI was found to be invariant to resolution, remaining consistently low, with an average of 0.06, 0.10, 0.14, 0.12, and 0.06 for the 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions respectively. The K562 cell line was found to have comparatively low proportional imbalances (Supplementary Figure 3). Such low PI gave precedence for the implementation of re-sampling prior to performing classification.

## DEVELOPING THREE TYPES OF PREDICTORS DESCRIBING THE ASSOCIATIONS BETWEEN TAD BOUNDARY REGIONS AND EPIGENOMIC FEATURES

A total of 78 cell type specific functional genomic annotations derived from ChIP-Seq experiments (See Methods) for the GM12878 and K562 cell line were used to build the feature space of downstream predictive models (Supplementary Tables 2-3). The annotations could be broken down into 3 sets including histone modifications (HM), chromatin state segmentations (ChromHMM), and transcription factor binding sites (TFBS). We constructed three different predictor types for each functional genomic annotation (Figure 1B). Counts of overlaps (**overlap count**, OC) were defined as the total number of peak regions that overlapped within a given genomic bin. Percents of overlaps (**overlap percent**, OP) were defined as the proportion of a bin overlapped by a peak region. **Distance** was defined as log2 transformed number of base pairs between between the centers of bins and regions defining genomic annotations. A log2-transformation of distance was used to account for the skewness present in the distributions of distances (Supplementary Figures 4-5).

## ENSEMBLE FRAMEWORK & COMPARISONS

In order to identify the combination of data resolution, predictor type, and re-sampling technique necessary for optimal cell line specific TAD boundary prediction, we created an ensemble framework to systematically compare performances of different model inputs (Figure 2). Each system in the framework was assumed to be composed of a random forest classifier constructed from a particular cell line (*L = {GM12878, K562}*). Within each cell line we evaluated 5 data resolutions (*R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*). We then considered 3 separate predictor types as the feature space (*P = {OC, OP, Distance}*). To assess the severity of class imbalance, 4 re-sampling techniques were implemented prior to modelling (*B = {None, RUS, ROS, SMOTE}*). Once the model inputs were established a random forest classifier was trained on chromosome specific sections of the genome using 10-fold cross validation. The model was then validated on the same separate chromosome specific test set for unbiased comparisons and evaluated using Matthews Correlation Coefficient (MCC). Letting $|X|$ denote the cardinality of each set, we evaluated *|L|* $\times$ *|R|* $\times$ *|P|* $\times$ *|B|* different ensemble systems, totaling 2520 (*2* $\times$ *5* $\times$ *3* $\times$ *4* $\times$ *21*) separate models. Additional performance metrics are reported in the supplementary materials.

![**Ensemble Framework.** A diagram of the ensemble framework detailing the combination of inputs used in the model building pipeline. Cell line specific TAD boundary data was extracted from a Hi-C produced contact matrix of a given resolution. A variety of functional genomic annotations were used to establish the feature space. Each subsequent random forest classification model was trained on an isolated predictor type in conjunction with a particular data re-sampling technique to account for class imbalance. Ten-fold cross validation was performed to tune for the number of predictor-type specific genomic features to consider at each node. Each model was then validated on a testing set and performances were evaluated using MCC.](Figures/figure3_ensemble_framework_V3.png)

## RANDOM FOREST CLASSIFIERS BUILT USING A DISTANCE-TYPE FEATURE SPACE COMBINED WITH SMOTE RE-SAMPLING PROVIDED OPTIMAL MODEL PERFORMANCE

<!--## CLASS IMBALANCE SEVERELY IMPACTS PERFORMANCE FOR CELL LINE SPECIFIC MODELS-->

When evaluating model performances, we found that regardless of resampling technique, random forest classifiers built using a distance-type feature space yielded consistently higher MCCs when compared to the other two predictor types (Figure 3). This indicated that models are better able to discriminate between TAD and non-TAD boundary regions when provided with spatially related associations. Delving further, we found that when combined with SMOTE re-sampling, random forest classifiers built using distance-type predictors out performed other re-sampling techniques across resolutions, suggesting that a combination of both random over- and under-sampling can improve TAD boundary prediction. Interestingly, given these parameters, we found that performances peaked at 10 kb resolution and then degraded as data resolution decreased. This reason for the improved performance between 5 kb and 10 kb data resolutions can be attributed to the added sparcity in the interaction frequency matrices at finer resolutions. This sparcity corresponds to inaccurate TAD calling which leads to worse model performance. Additionally, performances tended to be much more variable between chromosomes at lower resolutions. Moreover, this decreasing trend in performance was much more evident under the optimal combination of data level characteristics (SMOTE resampling with distance type predictors). These results imply that there is an ideal resolution in TAD boundary prediction, and that that an optimally performing cell line specific random forest classifier, one that is able to best discriminate between genomic bins that are near versus far away from TAD boundaries, is one that is built on 10 kb resolution data, with distance-type predictors, and incorporates both random under- and over-sampling. Models implemented on the K562 cell line were found to yield the same optimal data level characteristics (Supplementary Figure 6).

@@

## MODELS IMPLEMENTED ON TRANSCRIPTION FACTOR BINDING SITES, USING OPTIMAL PARAMETERS, OUTPERFORM OTHER ANNOTATION-SPECIFIC MODELS

We then aimed to compare the performances of annotation-specifc models. In doing so, we inspected the proportion of predictive importance that was explained by each of the 3 groups of annotations (HM, ChromHMM, and TFBS). For optimal random forest classifiers, we found that the majority of the proportional predictive importance was obtained by transcription factor binding sites (Supplementary Figure 7). This was consistent across resolutions, suggesting that TFBS were the primary drivers of TAD boundary formation in both the GM12878 and K562 cell lines.

We further assessed the predictive capabilities of the specific sets of annotations by comparing the performances of annotation-specific random forest models implemented on the optimal set of characteristics. We found that models built simply on TFBS outperformed other annotation-specific models at all resolutions (Figure 4A; Supplementary Figure 8A). Additionally, when compared to models built on all 3 sets of functional genomic annotations, the TFBS-specific models performed similarly at the 5 kb and 10 kb resolutions. Interestingly though, at the 25 kb, 50 kb, and 100 kb resolutions, the TFBS-specific models out performed models built on the combined sets of annotations. This indicated that, at lower resolutions, the inclusion of other types of annotations contributed to additional noise rather than signal in TAD boundary prediction.

##PREDICTIVE IMPORTANCES CONFIRMED BIOLOGICAL FUNCTIONALITY OF KNOWN ENRICHED TRANSCRIPTION FACTOR BINDING SITES AT TAD BOUNDARIES

Given that many TFBS are known to colocalize together on the linear genome and are therefore highly correlated, we sought to avoid the incidence of overfitting our optimally built classifier by performing recursive feature elimination (Supplementary Figure 9) to establish the necessary number of TFBS to include. We found that our cell line specific model was able to obtain near optimal performance using only ~8 TFBS (Figure 4B; Supplementary Figure 8B). However, given that we are modeling on chromosome specific sections of the genome, these 8 annotations are not the same for all chromosomes. To determine the most common TFBS, we clustered the predictive importances across chromosomes (Figure 4C; Supplementary Figure 8C). We found that the following transcription factors were most important in predicting TAD boundary regions: SMC3, ZNF143, CTCF, and RAD21. These are known architectural proteins responsible for the 3D structure of the human genome. Namely, the SMC3, CTCF, and RAD21 binding sites are known factors associated with the cohesin protein complex, which is hypothesized to be what creates loops in the DNA  [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self]. Likewise, ZNF143 is a known structural regulators of enhancer-promoter interactions that also contribute to looping of the linear genome [@weintraub2017yy1; @gonzalez2017znf143].

![**Assessing top ranked transcription factors in TAD boundary prediction.** (A) Barplots comparing performances of models using specific groups of functional genomic annotation as the feature space including histone modifications (HM; red), chromatin states (ChromHMM; green), transcription factor binding sites (TFBS; blue), in addition to a model with a feature space containing all 3 groups (Combined; purple). Error bars represent $\pm$ 1 standard deviation from the mean MCC across each chromosomal section of the linear genome. (B) Recursive feature elimimation analysis used to reduce the number of TFBS to include in the optimally build random forest classifier. Error bars represent 1 standard deviation away from the mean cross-validated MCC. (C) Clustered heatmap of variable importances for the union of the top 8 most predictive TFBS across chromosomes.](Figures/annot_specific_rfe_varimps_heatmap.png)

## LEVERAGING ChIP-seq PEAK REGIONS OF TOP PREDICTIVE TFBS PROVIDE MORE PRECISE LOCATION OF TAD BOUNDARIES

After obtaining our optimally built random forest classifier, we aimed to leverage the ChIP-seq peak regions defined by the SMC3, ZNF143, CTCF, and RAD21 tanscription factors for precised TAD bounday prediction at base pair resolution. We found that when we validated our model against chromosome specific base pairs, we were able to identify clusters of regions where the model predicted the base pair to be a TAD boundary with probability equal to 1. By clustering the regions and performing medoid partitioning (See Methods), we were able to identify a comparative number of TAD boundaries as the ARROWHEAD TAD caller. However, only 24% and 29% of predicted and called (and 10 kb flanked) TAD boundaries overlapped for the GM12878 and K562 cell line respectively, suggesting differing locations in TAD boundaries throughout the linear genome (Supplementary Figure 10). To compare between predicted and called TAD boundaries we evaluated the signal strength of ChIP-seq peak regions around a 10 kb flank of each. We found that the peak signal strength for the SMC3, ZNF143, CTCF, and RAD21 TFBS were much closer, on average, to our predicted TAD boudaries the the called TAD boundaries obtained using the ARROWHEAD pipeline for 10 kb resolution Hi-C data (Figure 5; Supplementary Figure ). ChIP-seq assays offer much higher resolutions (often in the tens of bases) compared to Hi-C sequenced data, which can be in the hundreds of kilobases. This disparity in resolution can affect a TAD caller's ability to precisely locate TADs. Moreover, by building a model using annotations known to be enriched at TAD boundaries we were able to bridge this gap in resolution and more precisely locate TAD boundaries that corresponded to the highest concentration in signal strength for top ranked TFBS.

![**Predicted TAD boundaries were centered closer to peak signal regions defined by known architectural transcription factors when compared to called TAD boundaries.** Enrichment heatmaps illustrate the average signal strength of ChIP-seq peak regions defined by (A) SMC3, (B) ZNF143, (C) CTCF, and (D) RAD21 around the centers of 10 kb flanked predicted and called TAD boundaries.](Figures/enrichment_heatmaps_gm12878.png)

>>>>

## A RESOLUTION-SPECIFIC APPROACH FOR PREDICTING TAD BOUNDARIES

We analyzed publically available replicate Hi-C data sets from the GM12878 and K562 cell lines (Supplementary Table 1). Topologically associating domains (TADs) were subsequently called using the ARROWHEAD pipeline [@durand2016juicer] at five data resolutions: 5 kb 10 kb, 25 kb, 50 kb, and 100 kb. After removing TADs that exceeded 2 md in length (biologically plausible maximum TAD size [??? Add ref, see one in SpectralTAD]), we obtained a total of 16133, 14824, 8081, 3560, and 919 unique TAD boundaries for the GM12878 cell line, and 9314, 10881, 6923, 3197, and 831 unique TAD boundaries for the K562 cell line across each of the five resolutions respectively (Supplementary Figure 1). To account for the variability in boundary location due to varying resolution, we developed a resolution-specific approach toward constructing TAD versus non-TAD boundary regions on the linear genome (See Methods), labeled as a response vector **Y** (Figure 1A). TAD boundary regions were defined as regions on the linear genome where a genomic bin overlapped with a flanked TAD boundary ($Y = 1$), while non-TAD boundary regions were defined as the regions that did not overlap with a flanked TAD boundary ($Y = 0$). A significant number [??? Need to put exactly, e.g., $18.34 \pm 5.06 \%$] of TAD boundary regions were found to be specific to one of the two cell lines (Supplementary Figure 2). Given the cell type specificity of TAD boundaries, we opted to build cell line specific models for predicting TAD boundary regions. The results presented are for the GM12878 cell line, with K562 results presented in the Supplementary material. In summary, we developed a framework enabling resolution-specific prediction of TAD boundaries, with resolution-specific bins defining the response variable.

![**Illustrating the resolution-specific data construction and feature engineering used for downstream modeling.** (A) Unique boundaries are denoted by the blue dots. The yellow regions denote the flanked boundary regions according to the Hi-C data resolution (i.e., 100 kb resolution corresponded to a 100 kb flank for a total boundary region of 200 kb). The linear genome was subsequently binned into resolution-specific intervals. The response vector **Y** was defined as a genomic bin that either overlapped with a flanked TAD boundary ($Y = 1$) or did not ($Y = 0$). (B) Three types of associations between bins and genomic annotations (green shapes) used to build the feature space include _Overlap Counts_ (OC), _Overlap Percent_ (OP), and ($log_{2}$) _Distance_. ](Figures/model_construction_and_predictor_types.png)

## THREE TYPES OF PREDICTORS DEFINE THE ASSOCIATIONS BETWEEN TAD BOUNDARY REGIONS AND GENOMIC ANNOTATIONS

A total of 78 cell type specific functional genomic annotations for the GM12878 and K562 cell line were used to build the feature space of downstream predictive models (Supplementary Tables 2-3). The annotations could be broken down into three sets including histone modifications (HM), chromatin state segmentations (ChromHMM), and transcription factor binding sites (TFBS). We constructed three different predictor types for each functional genomic annotation (Figure 1B). Counts of overlaps (**overlap count**, OC) were defined as the total number of genomic annotation regions that overlapped within a given genomic bin. Percents of overlaps (**overlap percent**, OP) were defined as the proportion of a bin overlapped by an annotation region. **Distance** was defined as log2 transformed number of base pairs between between the centers of bins and regions defining genomic annotations. A log2-transformation of distance was used to account for the skewness present in the distributions of distances (Supplementary Figures 4-5). These feature engineering steps were performed to improve TAD boundary predictions by accounting for direct (OC), proportional (OP), and indirect (distance) relationships between TAD boundaries and genomic annotations.

## TAD VS. NON-TAD BOUNDARY CLASS IMBALANCE IS SEVERE IRRESPECTIVELY OF Hi-C DATA RESOLUTION

Given that the number of bins annotated as TAD boundaries (TAD boundary regions) is much smaller than the number of non-TAD boundary bins, we investigated the class imbalance (CI) [??? I changed PI to CI - change in supplementary accordingly] featured at each resolution. The CI was defined as the ratio of TAD boundary regions ($Y=1$) versus the sum of both TAD and non-TAD boundary regions. The CI was found to be invariant to resolution, remaining consistently low, with an average of 0.06, 0.10, 0.14, 0.12, and 0.06 [??? Add exact numbers, like $18.34 \pm 5.06 \%$] for the Gm12878 data at 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions, respectively, with similar results observed for the K562 cell line  (Supplementary Figure 3). The presence of class imbalance justifies the the need for using resampling techniques before predictive modeling.

[??? Very briefly introduce each technique, refer to Methods for details]

## ENSEMBLE FRAMEWORK FOR TAD BOUNDARY PREDICTION

To identify the combination of data resolution, predictor type, and re-sampling technique necessary for optimal cell line specific TAD boundary prediction, we created an ensemble framework to systematically compare performances of different model inputs (Figure 2). The framework uses data for a particular cell line *L = {GM12878, K562}*, at a given resolution *R = {5 kb, 10 kb, 25 kb, 50 kb, 100 kb}*, using one of the predictor type *P = {OC, OP, Distance}*, and the re-sampling technique *B = {None, RUS, ROS, SMOTE}*. Once the model inputs were established, a random forest classifier was trained on chromosome-specific datasets using 10-fold cross validation. The model was then validated on the same separate chromosome specific test set for unbiased comparisons [??? Ugly sentence, rewrite] and evaluated using Matthews Correlation Coefficient (MCC). Letting $|X|$ denote the cardinality of each set, we evaluated $|L| \times |R| \times |P| \times |B|$ different ensemble systems, totaling $2 \times 5 \times 3 \times 4 \times 21 = 2520$) models. Additional performance metrics are reported in the Supplementary materials.

![**A diagram of the ensemble framework detailing the combination of inputs used in the model building pipeline.** [??? Describe abbreviations on the figure, the figure itself is already described in text] ](Figures/figure3_ensemble_framework_V3.png)

## SMOTE RESAMPLING, DISTANCE-BASED ASSOCIATIONS OF TAD BOUNDARIES AND GENOMIC ANNOTATIONS, AND 10KB RESOLUTION OF HI-C DATA PROVIDED OPTIMAL MODEL PERFORMANCE [??? This paragraph was completely rewritten, check for logic flow]

We investigated the effect of class imbalance on model performance using three re-sampling techniques. Expectedly, when using data as-is, that is, with class imbalance present, the models performed poorly. Using any of the resampling techniques improved the performance, with SMOTE-resampled data being the most optimal (Figure 3, Supplementary Figure 3). These results suggest that a combination of both random over- and under-sampling (SMOTE) can improve TAD boundary prediction.

We found that, regardless of resampling technique, random forest classifiers built using a distance-type feature space yielded consistently higher MCCs when compared to the overlap count and overlap percent predictor types (Figure 3), and these results were consistent across resolutions and cell types (Supplementary Figure 6). This indicated that models are better able to discriminate between TAD and non-TAD boundary regions when provided with spatially related associations.

Interestingly, we found that performances peaked at 10 kb resolution and then degraded as data resolution decreased. The reason for the improved performance between 5 kb and 10 kb data resolutions can be due to the sparsity in the interaction frequency matrices at finer resolutions. [??? Quantify sparsity, need to substantiate this statement] This sparsity may lead to inaccurate TAD calling and, subsequently, to worse model performance. These results suggest that finer resolution of Hi-C data is not always optimal for accurate TAD calling and prediction, and sparsity of the data needs to be considered.

Additionally, performances tended to be much more variable between chromosomes at lower resolutions. [??? Where are the results?] Moreover, this decreasing trend in performance was much more evident under the optimal combination of data level characteristics (SMOTE resampling with distance type predictors). [??? Where are the results?]

In summary, our results imply that using random under- and oversampling, distance-type predictors, and the data at 10kb resolution results in an optimally performing cell line-specific random forest-based TAD boundary prediction model.

@@

## TRANSCRIPTION FACTOR BINDING SITES OUTPERFORM OTHER ANNOTATION-SPECIFIC MODELS

We then aimed to compare the performances of annotation-specifc models. In doing so, we inspected the proportion of predictive importance that was explained by each of the three groups of genomic annotations (histone modifications (HM), chromatin states (ChromHMM), and transcription factor binding sites (TFBS)). For optimal random forest classifiers, we found that the majority of the proportional predictive importance was obtained by transcription factor binding sites (Supplementary Figure 7). Furthermore, models build solely on TFBSs outperformed other annotation-specific models at all resolutions (Figure 4A; Supplementary Figure 8A). Notably, the TFBS-specific models outperformed models built on the combined sets of annotations, and this effect was most pronounced at lower resolutions. This indicated that the inclusion of other types of annotations contributed to additional noise rather than signal in TAD boundary prediction. In summary, these results suggest that TFBS are the primary drivers of TAD boundary formation in both the GM12878 and K562 cell lines.

## PREDICTIVE IMPORTANCES CONFIRMED BIOLOGICAL FUNCTIONALITY OF CTCF, RAD21, SMC3, and ZNF143 AT TAD BOUNDARIES

Given that many TFBS are known to colocalize together on the linear genome and are therefore highly correlated (Supplementary Figure 9), we sought to avoid overfitting by performing recursive feature elimination. We found that our models were able to obtain near-optimal performance using approximately eight TFBSs (Figure 4B; Supplementary Figure 8B). However, given that we train our models on chromosome-specific data, the most significant annotations vary for each chromosome. To determine the most common TFBSs, we clustered the predictive importance values across chromosomes (Figure 4C; Supplementary Figure 8C). We found that, similar to other studies [@sanborn2015chromatin; @fudenberg2016formation; @alipour2012self; @weintraub2017yy1; @gonzalez2017znf143], CTCF, RAD21, SMC3, and ZNF143 transcription factors were most predictive of TAD boundary regions.

![**Assessing top ranked transcription factors in TAD boundary prediction.** (A) Barplots comparing performances of models using specific groups of functional genomic annotation as the feature space including histone modifications (HM; red), chromatin states (ChromHMM; green), transcription factor binding sites (TFBS; blue), in addition to a model with a feature space containing all three groups (Combined; purple). (B) Recursive feature elimimation analysis used to reduce the number of TFBS to include in the optimally build random forest classifier. (C) Clustered heatmap of variable importances for the union of the top 8 most predictive TFBS across chromosomes. Error bars represent standard deviation from the mean MCC across each chromosome.](Figures/annot_specific_rfe_varimps_heatmap.png)

## PREDICTIVE MODELING DEFINES PRECISE AND BIOLOGICALLY RELEVANT LOCATION OF TAD BOUNDARIES

After obtaining our optimally built random forest classifier, we investigated whether our predictive models can alleviate resolution limitations of Hi-C data by predicting TAD boundaries at base pair resolution. We were able to identify regions where the model predicted the base pair to be a TAD boundary with probability equal to 1. [??? Where is this figure? It seemed important] By clustering the regions (see Methods), we were able to predict a comparable number of TAD boundary regions as called by the ARROWHEAD TAD caller. However, only 24% and 29% of predicted and called (and 10 kb flanked) TAD boundaries overlapped for the GM12878 and K562 cell line, respectively, suggesting differing locations in TAD boundaries throughout the linear genome (Supplementary Figure 10). [??? Need further drill down, as we discussed]

For each predicted TAD boundary region, we were able to identify the summit locations of TAD boundary location by performing partitioning around medoids (see Methods). To compare the summit locations of predicted and called TAD boundaries, we evaluated the signal strength of ChIP-seq peak regions around a 10 kb flanking region. We found that the signal strength for the CTCF, RAD21, SMC3, and ZNF143 [??? Make all in this order!] TFBS peaked at our predicted TAD boudaries, while was poorly defined around the called TAD boundaries (Figure 5; Supplementary Figure [???]).  Thus, our model is able to alleviate resolution limitations and precisely locate TAD boundaries that correspond to the highest signal strength of known TAD boundary-forming TFBSs.

ChIP-seq assays offer much higher resolutions (often in the tens of bases) compared to Hi-C sequenced data, which can be in the hundreds of kilobases. This disparity in resolution can affect a TAD caller's ability to precisely locate TADs.[??? This is for the introduction, justifying motives for your work]

![**Predicted TAD boundaries are enriched in known TAD boundary-forming TFBSs.** Enrichment heatmaps illustrate the average signal strength of ChIP-seq peak regions defined by (A) SMC3, (B) ZNF143, (C) CTCF, and (D) RAD21 around the centers of 10 kb flanked predicted and called TAD boundaries.](Figures/enrichment_heatmaps_gm12878.png) [??? Order]
